Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-17 mr-review.Rmd
added snp assumptions from mraid

The estimated marginal effects for the $p$ SNP instruments on the exposure are denoted by $\hat \beta_X$, while 
$\hat\beta_Y$ represents the estimated effects of the same SNPs on the outcome. The $p$ by $p$ correlation matrices for 
the SNP instruments are written as $\Sigma_1$ and $\Sigma_2$, respectively. $\Sigma_1$ and $\Sigma_2$ can be estimated with 1000 Genomes 
Project data, for example, by choosing a subset of 1000 Genomes Project subjects that have similar ancestry 
[@the_1000_genomes_project_consortium_1000_2012]. The $p$-vector error terms, $e_x$ and $e_y$, follow multivariate normal 
distributions with mean zero and variances $\Sigma_1\frac{\sigma_X^2}{n_1 - 1}$ and $\Sigma_2\frac{\sigma_Y^2}{n_2 - 1}$, 
respectively.

>>>>

The estimated marginal effects for the $p$ SNP instruments on the exposure are denoted by $\hat \beta_X$, while 
$\hat\beta_Y$ represents the estimated effects of the same SNPs on the outcome. The $p$ by $p$ correlation matrices for 
the SNP instruments are written as $\Sigma_1$ and $\Sigma_2$, respectively. $\Sigma_1$ and $\Sigma_2$ can be estimated with 1000 Genomes 
Project data, for example, by choosing a subset of 1000 Genomes Project subjects that have similar ancestry 
[@the_1000_genomes_project_consortium_1000_2012]. The $p$-vector error terms, $e_x$ and $e_y$, follow multivariate normal 
distributions with mean zero and variances $\Sigma_1\frac{\sigma_X^2}{n_1 - 1}$ 
and $\Sigma_2\frac{\sigma_Y^2}{n_2 - 1}$, 
respectively. @yuan_likelihood_2021 then constructs a Gibbs sampler to make likelihood-based inferences [@geman1984stochastic]. To facilitate computations, the investigators make several assumptions about the collection of SNPs:

1. Relatively small proportion of SNPs have nonzero effects on the exposure  
1. A relatively small proportion of SNPs demonstrate horizontal pleiotropy  
1. The chosen instrumental SNPs are more likely to display horizontal pleiotropy than are non-instrumental SNPs  
1. Those SNPs that display horizontal pleiotropy are more likely to demonstrate uncorrelated horizontal pleiotropy than correlated horizontal pleiotropy.

By encoding these assumptions in prior distributions, @yuan_likelihood_2021 enables the inferential procedures to accommodate the observed data in the context of the assumptions on SNPs.
